---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,error = F,message = F,warning = F,
  comment = "#>",
  fig.path = "man/figures/README-"
)
```

# tidymeltt

There is a wealth of event history data out there. `tidymeltt` makes it easier to match and analyse disparate event datasets. 

[![Project Status: Active – The project has reached a stable, usable state and is being actively developed.](http://www.repostatus.org/badges/latest/active.svg)](http://www.repostatus.org/#active)

The goal of `tidymeltt` is to provide a robust and efficient toolkit for integrating, understanding, and visualizing georeferenced event data. `tidymeltt` builds off of the methodology of `meltt` (Merging Event Data by Location, Time, and Type) but disaggregates its properties, standardizes its syntax, and increases the efficiency of the integration task. More importantly, `tidymeltt` offers a library of functions to better understand spatio-temporal co-occurrence across entries from different datasets, which makes it easier to leverage co-occurrences to assess patterns regarding overlap and process.  

# Installation

**Note that the code is currently in production and is not currently stable.**

```{r,eval=F}
devtools::install_github("edunford/tidymeltt")
```



## Example

```{r example}
require(tidyverse)
require(tidymeltt)


# Generate Fake Spatio-Temporal Data
set.seed(123)
N = 100
dates = seq(from = as.Date("2007-01-01"),to=as.Date("2007-01-01"),by = "day")
lons = runif(N,0,.1)
lats = runif(N,0,.1)
d1 = data.frame(date = sample(dates,size = N,replace = T),latitude = sample(lats,N,T),longitude = sample(lons,N,T))
d2 = data.frame(date = sample(dates,size = N,replace = T),latitude = sample(lats,N,T),longitude = sample(lons,N,T))
d3 = data.frame(date = sample(dates,size = N,replace = T),latitude = sample(lats,N,T),longitude = sample(lons,N,T))
#d3$date[1:10] = NA


# Tidymeltt processing steps 

bundle(d1,d2,d3) %>% # Bundle together candidate datasets
define_space(.) %>% # define spatial features
define_time(d1="date",d2="date",d3="date") %>% # define temporal features 
define_close(.,space=2,time=1) -> xx # locate proximate entries (w/ no metadata disambiguation)

xx
```


# Development

## To Dos

- `define_ space/time`: build specific classes for each feature type.
- `missing()`: build a singular function that reports missingness in the feature set.
- `nearby()`: select space/time with class rather than name.
- `partner()`: 
    + gather tax elements with class. 
    + build assessment
- rename `partner()` to `def_match()`
- rename `nearby()` to `def_close()`


## Consider Some Prefix Changes (for simplicity)

- Changing `define_` to `def_`

- Organizing logic centers around a series of `def_` functions (computation/production functions) and `get_` functions (data retrieval functions)
    + `def_`
        - `def_time()` - what is time?
        - `def_space()` - what is space?
        - `def_taxonomy()` - what variables should entries be compared on?
        - `def_close()` - what constitutes "close"?
        - `def_match()` - which events match, given `def_close()` & `def_taxonomy()`
    + `get_`
        - `get_missing()` - what data is missing from the evaluation features?
        - `get_close()` - return data with an index marking all entries that are "near" to other entries in the other bundled datasets.
        - `get_matches()` - return all data that matched up; also, `get_duplicates()`. Same function.
        - `get_unique()` - return all data with duplicate entries removed. 
        - `get_data()` - return unbundled data along with any requested features. Also, `unbundle()`.
        
     

